### 2015-06-10 doc/notebook/2015-02-26_Bacterial_data_acquisition.Rmd
Output metadata with quotes to facillitate reading back in

write.table(metadata_good, file="data/mothur/bacteria.good.metadata", quote=F, sep="\t")
```

@@

write.table(spread_sheet_good[,colnames(metadata_good)], file="data/mothur/bacteria.good.metadata", quote=F, sep="\t", col.names=F, append=T)
```

>>>>

write.table(metadata_good, file="data/mothur/bacteria.good.metadata", quote=TRUE, na="NA", sep="\t")
```

@@

write.table(spread_sheet_good[,colnames(metadata_good)], file="data/mothur/bacteria.good.metadata", quote=TRUE, na="NA", sep="\t", col.names=F, append=T)
```
